Deciding to Disclose

### 2015-09-15 Conclusion.tex
We mean midwives with the example

From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant. There is a high level of uncertainty in the overall dynamics with the model free rules. This does not arise with the more complex rules, because they reframe information from others in the context of their own experiences, as what would happen to them in that situation. By contrast, the simpler rules treat the experiences as having literally happened to them, and since there is no mechanism of homophily, no way to listen only to accounts of agents similar to themselves, they can come to believe unreasonable things.Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models. While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model. This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.

>>>>

From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant. There is a high level of uncertainty in the overall dynamics with the model free rules. This does not arise with the more complex rules, because they reframe information from others in the context of their own experiences, as what would happen to them in that situation. By contrast, the simpler rules treat the experiences as having literally happened to them, and since there is no mechanism of homophily, no way to listen only to accounts of agents similar to themselves, they can come to believe unreasonable things. Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models. While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model. This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.

### 2015-09-15 Model.tex
We mean midwives with the example

In the disclosure game model, this takes the form of having each agent recount their play history to their colleagues with some probability \(q\). Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e. \(n_{j} = n_{j} + w\)).
Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.}

>>>>

In the disclosure game model, this takes the form of having each agent recount their play history to their colleagues with some probability \(q\). Individuals then incorporate shared information into their beliefs using weighted updates, e.g. for a midwife a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e. \(n_{j} = n_{j} + w\)).
Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.}
